Calendar-based graphics for visualizing people's daily schedules

### 2017-08-08 main.Rmd
fixed the cap in figure 5

(ref:month-diagram-cap) Illustration of the indexing layout for cells in a month. $k$ is day of the week, $g$ is day of the month, $i,j$ indicates grid position.

>>>>

(ref:month-diagram-cap) Illustration of the indexing layout for cells in a month, where $k$ is day of the week, $g$ is day of the month, $i,j$ indicates grid position.

### 2017-08-08 main.tex
fixed the cap in figure 5

\begin{equation}
  \begin{aligned}
  i &= \lceil (g \mod 35) / 7\rceil, \\
  j &= g \mod 7. \label{eq:grid}
  \end{aligned}
\end{equation}

@@

\caption[Illustration of the indexing layout for cells in
a month. \(k\) is day of the week, \(g\) is day of the month, \(i,j\)
indicates grid position.]{Illustration of the indexing layout for cells in
a month. \(k\) is day of the week, \(g\) is day of the month, \(i,j\)
indicates grid position.}\label{fig:month-diagram}
\end{figure}
\end{CodeChunk}

>>>>

\begin{equation}
  \begin{aligned}
  i &= \lceil (g\,\mod 35) / 7\rceil, \\
  j &= g\,\mod 7. \label{eq:grid}
  \end{aligned}
\end{equation}

@@

\caption[Illustration of the indexing layout for cells in
a month, where \(k\) is day of the week, \(g\) is day of the month,
\(i,j\) indicates grid position.]{Illustration of the indexing layout for cells in
a month, where \(k\) is day of the week, \(g\) is day of the month,
\(i,j\) indicates grid position.}\label{fig:month-diagram}
\end{figure}
\end{CodeChunk}
